scikit-image, a Python library for 2D and 3D image processing

### 2016-08-16 skimage_tomo.tex
Various wording suggestions

Several software applications and libraries are available to synchrotron
users to process their images. ImageJ~\citep{Abramoff2004, Schneider2012}
and its distribution Fiji~\citep{Schindelin2012} is a popular tool for
2-D and 3-D images, thanks to its intuitive menus and graphical tools,
and the wealth of plugins contributed by a vivid
community~\citep{Schindelin2015}. For 3-D images, commercial tools such
as Avizo 3D software (TM) are appreciated for an intuitive graphical
pipeline and advanced 3D visualization. Alternatively, the use of a
programming language gives finer control and more possibilities, provided
classical processing algorithms can be called from libraries -- hence
limiting the programming task and the risk of bugs. Matlab (TM) and its
image processing toolbox are popular in the academic community of
computer vision and image processing. The Python language is widely used
in the scientific world and in synchrotron facilitiies. As a
general-purpose language, Python is used in synchrotrons for controlling
device servers~\citep{pytango}, reconstructing tomography volumes from
radiographies~\citep{Gursoy2014, Mirone2014}, and various data
processing packages for macromolecular cristallography~\citep{Adams2010},
azimuthal integration of diffraction data~\citep{Ashiotis2015} or
fluorescence analysis~\citep{pymca}.

\texttt{scikit-image}~\citep{Vanderwalt2014} is a general-purpose image
processing library for the Python language, and a component of the ecosystem of
Python scientific modules commonly known as Scientific
Python~\citep{Oliphant2007}. Like the rest of the ecosystem,
\texttt{scikit-image} is released under a permissive open-source license and is
available free of charge. \texttt{scikit-image} is compatible with both 2-D and
3-D images, so that it can be used for a large number of imaging modalities,
such as microscopy, radiography or tomography. In this article, we explain how
\texttt{scikit-image} can be used for processing data acquired in synchrotron
imaging experiments, with a strong focus on microtomography 3-D images. This
article does not intend to be a pedagogical tutorial on \texttt{scikit-image}
for X-ray imaging, but rather to explain the rationale behind the package, and
what can be done with \texttt{scikit-image}.

@@

Image are manipulated as numerical arrays of uniform
data type, a format that guarantees a fast access to the computer memory. The
n-dimensional (2-D, 3-D, \dots) numerical array object is provided by the
\texttt{NumPy} module~\citep{Vanderwalt2011}.

In image processing, one of the first tasks is therefore to generate
\texttt{NumPy} arrays, which is often done by reading data from files. Let us
read one 2-D image from a file and display it with the following lines of code:

@@

The benefits of \texttt{scikit-image} for image processing come not only
from the features of the package alone, but also from the rich
environment of Scientific Python~\citep{Oliphant2007, Perez2011}.
Fig.~\ref{fig:ecosystem} illustrates how several components of this
ecosystem are used for a typical image processing workflow.

>>>>

Several software applications and libraries are available to synchrotron
users to process their images. ImageJ~\citep{Abramoff2004, Schneider2012}
and its distribution Fiji~\citep{Schindelin2012} is a popular tool for
2-D and 3-D images, thanks to its intuitive menus and graphical tools,
and the wealth of plugins contributed by a vivid
community~\citep{Schindelin2015}. For 3-D images, commercial tools such
as Avizo 3D software (TM) are appreciated for an intuitive graphical
pipeline and advanced 3D visualization. Alternatively, the use of a
programming language gives finer control and more possibilities, provided
classical processing algorithms can be called from libraries -- hence
limiting the programming task and the risk of bugs. Matlab (TM) and its
image processing toolbox are popular in the academic community of
computer vision and image processing. The Python language is widely used
in the scientific world and in synchrotron facilities. As a
general-purpose language, Python is used in synchrotrons to control
device servers~\citep{pytango}, to reconstruct tomography volumes from
radiographs~\citep{Gursoy2014, Mirone2014}, and in data
processing packages for macromolecular cristallography~\citep{Adams2010},
azimuthal integration of diffraction data~\citep{Ashiotis2015} or
fluorescence analysis~\citep{pymca}.

\texttt{scikit-image}~\citep{Vanderwalt2014} is a general-purpose image
processing library for the Python language, and a component of the ecosystem of
Python scientific modules commonly known as Scientific
Python~\citep{Oliphant2007}. Like the rest of the ecosystem,
\texttt{scikit-image} is released under a permissive open-source license and is
available free of charge. Most of \texttt{scikit-image} is compatible with both 2-D and
3-D images, so that it can be used for a large number of imaging modalities,
such as microscopy, radiography or tomography. In this article, we explain how
\texttt{scikit-image} can be used for processing data acquired in synchrotron
imaging experiments, with a strong focus on microtomography 3-D images. This
article does not intend to be a pedagogical tutorial on \texttt{scikit-image}
for X-ray imaging, but rather to explain the rationale behind the package, and
provide various examples of its capabilities.

@@

Images are manipulated as numerical arrays of uniform
data type, a format that guarantees a fast access to the computer memory. The
n-dimensional (2-D, 3-D, \dots) numerical array object is provided by the
\texttt{NumPy} module~\citep{Vanderwalt2011}.

In image processing, one of the first tasks is therefore to generate
\texttt{NumPy} arrays, which is often done by reading data from files. We
read one 2-D image from a file and display it with the following lines of code:

@@

The benefits of \texttt{scikit-image} for image processing come not only
from the features of the package alone, but also from the rich
environment of Scientific Python~\citep{Oliphant2007, Perez2011}.
Fig.~\ref{fig:ecosystem} illustrates how several components of this
ecosystem combine into a sophisticated image processing workflow.
